Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-08-30 ms/manuscript.Rmd
Lump small bioregions in MS

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::word_document2:
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
    toc: no
    number_sections: no
    reference_docx: template.docx
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
params:
  doc_type: doc
editor_options: 
  chunk_output_type: console
---

@@

Short running title: Biodiversity of Japanese ferns

@@

```{r bioregions-make}
# Taxonomic bioregions
a <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = taxonomic_cluster), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(a)** Taxonomic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Cluster") +
  scale_fill_manual(values = bioregion_cols) +
  map_theme()

# Phylogenetic bioregions
b <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = phylo_cluster), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(b)** Phylogenetic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Cluster") +
  scale_fill_manual(values = bioregion_cols) +
  map_theme() +
  theme(axis.text.y = element_blank())

@@

**`r figure("bioregions")`**. Bioregions of the ferns of Japan. (a), taxonomic bioregions. (b), phylogenetic bioregions. Bioregions determined by clustering taxonomic (Sørensen) or phylogenetic (PhyloSor) distances into *k* = 8 or 7 groups, respectively.

>>>>

---
title: "Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::word_document2:
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
    toc: no
    number_sections: no
    reference_docx: template.docx
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "apa-6th-edition.csl"]
params:
  doc_type: doc
editor_options: 
  chunk_output_type: console
---

@@

Short running title: Spatial phylogenetics of Japanese ferns

@@

```{r bioregions-make}
# Lump regions with just a few cells (3 or less)
biodiv_ferns_spatial_lumped <-
biodiv_ferns_spatial %>%
  mutate(taxonomic_cluster = fct_lump_min(taxonomic_cluster, 4))  %>%
  mutate(phylo_cluster = fct_lump_min(phylo_cluster, 4))

# Taxonomic bioregions
a <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial_lumped, aes(fill = taxonomic_cluster), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(a)** Taxonomic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Cluster") +
  scale_fill_manual(values = bioregion_cols) +
  map_theme()

# Phylogenetic bioregions
b <- ggplot() +
  geom_sf(data = japan, fill = "white", color = "transparent", lwd = coast_lwd) +
  geom_sf(data = biodiv_ferns_spatial_lumped, aes(fill = phylo_cluster), color = "transparent") +
  geom_sf(data = japan, fill = "transparent", color = coast_col, lwd = coast_lwd) +
  annotate(geom="richtext", y = Inf, x = -Inf, label = "<span style='color:black'>**(b)** Phylogenetic</span>", hjust = "inward", vjust = "inward", color = "white") + 
  labs(fill = "Cluster") +
  scale_fill_manual(values = bioregion_cols) +
  map_theme() +
  theme(axis.text.y = element_blank())

@@

**`r figure("bioregions")`**. Bioregions of the ferns of Japan. (a), taxonomic bioregions. (b), phylogenetic bioregions. Bioregions determined by clustering taxonomic (Sørensen) or phylogenetic (PhyloSor) distances. Bioregions with three or fewer grid cells are lumped into the "Other" category.
